\MakeUppercase{Linear versus centred chromatic numbers}\thanks{This research was partly funded by NSERC.}

### 2022-05-30 lin-vs-cen.tex
Fixed sentence in Ack

The main subject of this paper was posed as an open problem at the 9th Annual Bellairs Workshop on Geometry and Graphs (v2), which was held January 21--28, 2022 and again at the 16th Annual Workshop on Probability and Combinatorics, which was held March 25--April 1, 2022. We are grateful to the organizers and participants of both workshops for providing a stimulating research environment.
Pat~Morin especially enjoyed early-morning discussions with Stefan~Langerman on the Seabourne Terrace and to Omer Angel for pointing out that the problem on $k\times k$ grid has a simple solution.

>>>>

The main subject of this paper was posed as an open problem at the 9th Annual Bellairs Workshop on Geometry and Graphs (v2), which was held January 21--28, 2022 and again at the 16th Annual Workshop on Probability and Combinatorics, which was held March 25--April 1, 2022. We are grateful to the organizers and participants of both workshops for providing a stimulating research environment.
Pat~Morin especially enjoyed early-morning discussions with Stefan~Langerman on the Seabourne Terrace. We are also grateful to Omer Angel for pointing out that the problem on $k\times k$ grid (as opposed to pseudogrid) has a simple solution.
